MSDS6372 - Final Project

### 2018-03-30 MSDS6372_Final_Project_BBHOF.Rmd
Updated PCs to output only 4

# display top 5 and bottom 5 observations
knitr::kable(BBHOFRaw[1:10,],caption = "Top 10 Observations from Baseball Hall of Fame Data", row.names = FALSE, "html") %>%
  kable_styling(bootstrap_options = c("striped","hover"))

@@

# perform PCA
BBHOF_PCA <- prcomp(BBHOF_PCA, center=TRUE, scale.=TRUE)
# since the labels also include 2, converting those to 1, so the result is truly binary (1, 0)
BBHOF_Labels_PCA$HOFMembership[BBHOF_Labels_PCA$HOFMembership == 2] <- 1

# print principal components
print(BBHOF_PCA)

>>>>

# display top 5 observations
knitr::kable(BBHOFRaw[1:5,],caption = "Top 10 Observations from Baseball Hall of Fame Data", row.names = FALSE, "html") %>%
  kable_styling(bootstrap_options = c("striped","hover"))

# display frequency table for did/did not get inducted into HOF
# since the labels also include 2, converting those to 1, so the result is truly binary (1, 0)
BBHOFRaw$HOFMembership[BBHOFRaw$HOFMembership == 2] <- 1
count(BBHOFRaw, "HOFMembership")

@@

# perform PCA
BBHOF_PCA <- prcomp(BBHOF_PCA, center=TRUE, scale.=TRUE)

# print principal components (only the first 4 PCs)
print(BBHOF_PCA$rotation[,1:4])
